Instructions for \confname{} Proceedings

### 2019-05-06 papers/EMNLP2019/many_names.tex
small change, text git integration
updates in spellchecking, new findings in analysis

\subsection{Disagreement}

Why and when do speakers disagree in their object naming choices. We first propose a qualitative analysis here.

\begin{itemize}
\item \textbf{synonyms}: e.g.\ aircraft vs. airplane 
\item \textbf{taxonomic levels}: e.g.\ man vs. person
\item \textbf{cross-classification}: e.g.\ chicken vs. dinner
\item \textbf{conceptual disagreement}: e.g.\ swan vs. goose
\end{itemize}

@@

>>>>

Why is naming more flexible in certain domains than in others?

\subsection{Lexical relations}

In this section, we take a closer look at the lexical variation we observe in our data set. We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain. \sz{domains need to be updated}

The naming variants can be grouped according to their lexical relation, as follows:

\begin{itemize}
\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
\item \textbf{hyponymy}: e.g.\ man vs. person
\item \textbf{co-hyponymy}: e.g.\ chicken vs. dinner, swan vs. goose
\item \textbf{no relation}: e.g.\  desk vs. apple
\end{itemize}

\begin{table}
\small
\begin{tabular}{llll}
\toprule
        relation & \% types & \% tokens & av. depth \\
\midrule
 co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
    hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
        synonymy &  0.015 &  0.121 &       1.000 \\
\bottomrule
\end{tabular}
\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?}}
\label{tab:rel}
\end{table}

Research on object naming following the idea of entry-level categories has, essentially, exclusively looked at names that stand in a hierarchical relation (i.e.\ hyponymy/hypernymy).

We use WordNet to extract lexical relations between the naming variants in our data set.
Unfortunately, this means that we have to exclude a certain portion of the data as either (i) one of the name is not covered in WordNet, (ii) we cannot find a lexical relation between the two names (see below). Also, we had to be relatively permissive with respect to the definition of hyponymy/co-hyponymy. 
For instance, to analyze \textit{giraffe} as a hyponym of \textit{animal} we have to look at the closure of the hyponyms of \textit{animal} with a depth of 8 (in WordNet).

\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.}

Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet, for types and tokens of naming variants respectively. \sz{Is it clear what types and tokens mean here? probably not...}

\subsection{Issues with WordNet}

%\begin{itemize}
%\item \textbf{synonyms}: e.g.\ aircraft vs. airplane 
%\item \textbf{taxonomic levels}: e.g.\ man vs. person
%\item \textbf{cross-classification}: e.g.\ chicken vs. dinner
%\item \textbf{conceptual disagreement}: e.g.\ swan vs. goose
%\end{itemize}

@@

\begin{table*}
\small
\begin{tabular}{lp{12cm}}
\toprule
                         category &                                                                                                                                                                                                                    most frequent naming variants \\
\midrule
 food, solid food &  sandwich -- food (492), hotdog -- food (467), hotdog -- sandwich (318), cake -- food (265), bread -- sandwich (257), bread -- food (247), bread -- bun (206), donut -- food (188), hotdog -- bun (184), sandwich -- burger (163) \\
 structure, construction &  house -- building (1160), building -- house (511), bridge -- train (326), bridge -- overpass (235), house -- window (161), house -- home (123), tent -- canopy (120), building -- castle (101), bridge -- building (98), bridge -- pole (85) \\
 tool &  knife -- pizza (27), knife -- food (22), knife -- cake (17), knife -- banana (16), knife -- plate (15), knife -- apple (13), knife -- pocket knife (12), knife -- butter knife (12), knife -- table (10), knife -- carrot (8) \\
 vehicle &  airplane -- plane (11194), plane -- airplane (3829), motorcycle -- bike (2624), airplane -- jet (1319), boat -- ship (1301), truck -- car (1095), car -- vehicle (874), motorcycle -- wheel (861), truck -- vehicle (718), truck -- wheel (716) \\
 plant, flora, plant life &  flower -- flowers (29), rose -- flower (25), flower -- rose (22), flower -- vase (18), flowers -- flower (14), flower -- dandelion (14), plant -- flower (12), flower -- sunflower (11), plant -- wheat (11), flower -- flower pot (10) \\
 food, nutrient &  pizza -- food (1796), sandwich -- food (631), pizza -- cheese (447), pizza -- plate (423), salad -- food (402), sandwich -- burger (235), pizza -- toppings (217), pizza -- pizza slice (162), sandwich -- bread (156), food -- sandwich (147) \\
 tableware &  cup -- mug (146), mug -- cup (104), cup -- coffee (93), cup -- drink (73), bowl -- food (60), cup -- glass (39), bowl -- cup (36), glass -- wine glass (35), glass -- cup (34), cup -- coffee cup (31) \\
 article of clothing &  shirt -- t-shirt (2914), jacket -- coat (2396), jacket -- shirt (1552), jacket -- suit (1168), suit -- jacket (1029), shirt -- jacket (813), shirt -- tie (723), shirt -- man (487), shirt -- dress (462), shirt -- sweater (450) \\
 animal &  cow -- bull (515), sheep -- goat (486), cow -- animal (445), giraffe -- animal (380), bird -- parrot (349), sheep -- animal (294), sheep -- lamb (282), horse -- animal (269), cat -- animal (237), bird -- seagull (231) \\
 ware &  fork -- spoon (71), fork -- plate (44), spoon -- food (32), fork -- food (31), fork -- cake (21), spoon -- fork (18), spoon -- wooden spoon (15), fork -- broccoli (15), fork -- silverware (10), spoon -- vegetables (8) \\
 person &  woman -- person (3594), man -- person (3546), boy -- child (3243), woman -- girl (2328), girl -- child (1985), woman -- tennis player (1277), man -- player (1273), man -- boy (1214), skateboarder -- skater (1194), man -- t-shirt (1143) \\
 instrumentality, instrumentation &  couch -- sofa (4090), desk -- table (3435), carpet -- floor (1697), bench -- chair (1401), desk -- keyboard (1380), counter -- table (1201), table -- desk (1135), counter -- countertop (1101), table -- counter (906), rug -- carpet (895) \\
\bottomrule
\end{tabular}\caption{Most frequent naming variants for each category}
\label{tab:exvariants}
\end{table*}
